Operation Mode Study in Cloud Manufacturing Ecosystem

### 2016-09-09 background.tex

platform model is about the part of decision making	agent of platform.

@@

user's model is the part of decision making agent of users.

@@

the core is about the decision making all the time, individuals' decision making will affect themselves directly, that will lead to most of the microscopic evolution, and the group effective will contribute part of the macroscopic evolution

@@

so, the topic here is the design of both decision making agents.
% subsection the_evolution_of_manufacturing_ecosystem (end)
% section background (end)

>>>>

platform model is about the part of decision-making	agent of platform.

@@

user's model is the part of decision-making agent of users.

@@

the core is about the decision-making all the time, individuals' decision-making will affect themselves directly, that will lead to most of the microscopic evolution, and the group effective will contribute part of the macroscopic evolution

@@

so, the topic here is the design of both decision-making agents.
% subsection the_evolution_of_manufacturing_ecosystem (end)
% section background (end)

### 2016-09-09 design.tex

% !TEX root = Eco-Model.tex
\section{Design of the ecosystem} % (fold)
\label{sec:design_of_the_ecosystem}
\subsection{Preliminaries} % (fold)
\label{sub:preliminaries}
Before the design of the ecosystem, we specify some basic concepts: 
\begin{compactitem}
	\item Provider: the individual who provide resource;
	\item Resource: the basic task process object with renewable capacity and unique type;
	\item Demander: the individual who publish order that contain bunch of tasks;
	\item Order: the task bundle like a project;
	\item Task: the basic object need to be processed with certain type and capacity of resource;
	\item Task-part: virtual segmentation unit of one task;
	\item Product: the perform result of task;
	\item Platform: the place where individual interact with other and environment.
\end{compactitem}

With the cloud manufacturing platform operating, demander publish order while provider provide resource, then they make decisions to  arrange the resources to perform tasks that decomposed from order. Most recent researchers like Wu et al.\cite{Wu2013} describe this operation procedure in cloud manufacturing as a tri-group user model that contains:\begin{inparaenum}[1)]
\item users/customers,
\item application providers and
\item physical resource providers.
\end{inparaenum}
Inspired by this model, we design the original operation mode shown in \autoref{fig:originmode} as the basis.
\begin{figure}[htbp]
    \centering
    \resizebox{0.9\textwidth}{!}{\input{figures/origin_mode}}
    \caption{Original mode}
    \label{fig:originmode}
\end{figure}
In this mode, individual executes activities that interact with others depicted by object flow(full lines) and information flow(dashed lines). The demander publish order that can be described by an activity-on-node(AON) network where the node represent the task and the arc the precedence relation. Each task needs to be performed with pre-determined configuration of resources. Hence, even after response and assign procedure, the selected resource cannot start to process the task until all of other selected resources are ready, we call this procedure as resource cooperation and what each resource actually process is the task-part, which is a virtual segmentation of one task, it just like if we run one program in cloud computing platform, we actually use some quota of provider A's DB and some quota of provider B's CPU, we can consider these as task-parts. Product, the performance result after the process and assembly procedure, will be delivered to demander, then demander change the rank value of the selected resource owners according to the review of the product. Cooperation procedure is necessary because of resource capacity is limited, but task-parts belonging to one task should be processed simultaneously to make sure the required resource capacities are available. We call the task-part is active when being processed, semi-active when selected resource is cooperating, inactive when this part is just assigned to the job queue.

\subsubsection{Assumptions} % (fold)
\label{ssub:assumptions_nomenclature}
To scope our research, we make some assumptions as follows for the original mode, while in other extension, some of the assumptions will be modified.
\begin{compactitem}
\item Each single task should be assembled by its task-parts, and these parts should be processed simultaneously;
\item The quality of product is determined by the worst quality of the selected resource;
\item Resource are renewable that the available capacity will be return to when the process procedure finished;
\item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
\item Cooperate and process procedure cannot be interrupted;
\item Provider can only schedule task-parts in inactive status. 
\end{compactitem}

@@

	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$, determined by order and some assign procedure\\

@@

$(i,j,k,l,\alpha)$. When in schedule procedure, we omit subscript $i$ for some reasons in \autoref{sub:schedule_the_jobs_in_machine}.

@@

\subsection{Individual decisions in original mode} % (fold)
\label{sub:interactions_and_decisions}
\subsubsection{Provider response for type matched task}
\label{subs:Response_for_type_matched_task}
Provider makes decision at time $\tau\ge r_i$ to response task if the belonging resource $mr_k$ was type matched with $t_{ij}$ ($P(mr_k)\in\mathcal{A}_{ij}$). If $A_{k,\tau} \ge q_{\alpha,ij}$, provider will response the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{ij,\tau}$. If $mr_k$ was finally selected, available capacity of $mr_k$ will change as $A_{k,\tau} := A_{k,\tau} - q_{\alpha,ij}$, the available capacity will be returned back to after the finish of $t_{ij}$ part.

\subsubsection{Demander select from resource candidates}
\label{subs:select_resource_candidates}
Demander make decision about resource selection from $\mathcal{R}_{ij,\tau}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$. Without loss of generality, we suppose at time $\tau \ge r_i$, the decision making of demander can be described as follows:
\begin{equation}
\max_{\forall \bm{k}}\left( \delta_{\bm{k}}, 
R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
\right) \label{eq:selectresaim}
\end{equation}
\begin{numcases}{\text{s.t.}}
q_{\alpha,ij} \le C_{k_{\alpha},\tau} & $\alpha\in\mathcal{A}_{ij}$\label{eq:rescaplimit}\\
\mathcal{R}_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & $\alpha\in\mathcal{A}_{ij}$\label{eq:restypeabstract}\\
\mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \label{eq:nrc}\\
\bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right] & \label{eq:decisionvectork}\\
k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &$\alpha\in\mathcal{A}_{ij}$ \label{eq:decisionvark}
\end{numcases}

The multi-objective in \autoref{eq:selectresaim} aims at high quality, high resource owner rank and low waiting queue length. \autoref{eq:rescaplimit} makes sure that resource capacity is capable to process the task part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variable, the demander should make decision to select resource in each type.

@@

\subsection{Incubation mode} % (fold)
\label{sub:incubation_mode}
Incubation mode is one extension on the original mode, the purpose of this mode is to remove the cooperate and assembly procedure in advance by gathering types of resources with certain quota into manufacturing service, which will be incubated as shown in \autoref{fig:serviceincubatemode}.  
\begin{figure}[htbp]
    \centering
    \resizebox{0.7\textwidth}{!}{\input{figures/service-incubate}}
    \caption{Incubation mode}
    \label{fig:serviceincubatemode}
\end{figure}
After the finish of task-part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such task-specified service for the future performance.

The first thing of incubation is to publish a job named \textbf{service-call}, which is similar with task except for the capacity dominance feature , which means capacity of selected resource will not be returned back to after the performance of service-call. The process result of one service-call is manufacturing \textbf{service}, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resource with same type to make contribution to the formation of one service. No more cooperate and assembly procedure are part of pros of service and product quality will no more restricted to the worst quality of resources for the complementary effect, while the cons of service include that service can only perform specified task.
Now we can classify task and service-call into \textbf{job}, resource and service into \textbf{machine} for the follow discuss.

\subsubsection{Provider response for type matched job} % (fold)
\label{ssub:response_in_type_matched_resource}
Apart from $mr_k$ response for $t_{ij}$ as we explained in \autoref{subs:Response_for_type_matched_task}, there are 2 other cases in incubation mode:
\begin{asparaenum}
\item $mr_k$ response for $sc_l$
\suspend{asparaenum}
If $mr_k$ was type matched with $sc_l$ ($P(mr_k)\in\mathcal{A}_l$), as long as $C_{k,\tau}> 0$, provider of $mr_k$ will response the service-call. If $mr_k$ was finally selected, both available capacity and capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and these capacity will not be returned back even after the finish of $sc_l$ part. Provider of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{l,\tau}$.
\resume{asparaenum}
\item $ms_l$ response for $t_{ij}$
\end{asparaenum}
Service is task-oriented machine, so if type matched ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of it will response $t_{ij}$ as soon as possible, demander will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.

@@

Similar to other situations, \autoref{eq:combaim} is a multi-objective function that aims at high quality, high rank and low waiting queue length. \autoref{eq:optk} and \autoref{eq:optl} are the optimal decision in independent conditions, \autoref{eq:temprank}, \autoref{eq:templength} and \autoref{eq:tempqualitystart} are the virtual rank value, virtual queue length and virtual quality value that are set in the worst cases.\autoref{eq:tempqualitystart}--\ref{eq:tempqualityend} are the virtual quality value calculate procedure. \autoref{eq:newdicisionvariable} is the decision to choose one of these two partial optimal decision.

@@

In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{(s)}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}}$. Since the task in $\mathcal{L}^{(s)}_{k,\tau_0},\mathcal{H}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, we ignore the type subscript $\alpha$ because all the job assigned here are already type matched. The schedule model is:

@@

% \subsection{Tricky problem} % (fold)
% \label{sub:tricky_problems}
% Even though the schedule procedure exclude the interference of service-call, one tricky problem will occur that it will block some tasks from being processed. Suppose that $t_{i1}$ and $t_{i2}$ both need resource $mr_1$ and $mr_2$, as shown in \autoref{fig:joblock}, 
% \begin{figure}[htbp]
% 	\centering
% 	\resizebox{.75\textwidth}{!}{\input{figures/job-lock}}
% 	\caption{Simple illustration of job lock problem}
% 	\label{fig:joblock}
% \end{figure}
% $t_{i2}$ is semi-active in $mr_2$ and inactive in $mr_1$, while $t_{i1}$ is semi-active in $mr_1$ and inactive in $mr_2$, however, there is no more space for inactive tasks to stack in, so no matter how long the resource will wait, $t_{i1}$ and $t_i2$ will not be processed and they will block the other tasks from being processed.

>>>>

% !TEX root = Eco-Model.tex
\section{Design of the ecosystem} % (fold)
\label{sec:design_of_the_ecosystem}
% \subsection{Preliminaries} % (fold)
% \label{sub:preliminaries}
Before introducing the design of the ecosystem, we specify some basic concepts:
\begin{compactitem}
	\item Provider: the individual who provides resource;
	\item Resource: the basic task process object with renewable capacity and unique type;
	\item Demander: the individual who publishes orders that contain bunch of tasks;
	\item Order: the task bundle like a project;
	\item Task: the basic object that needs to be processed with certain type and capacity of resource;
	\item Task-part: virtual segmentation unit of one task;
	\item Product: the perform result of a task;
	\item Platform: the place where individuals interact with other and ecosystem.
\end{compactitem}

With the cloud manufacturing platform operating, demanders publish orders while provider provide resources, then they make decisions to  arrange the resources to perform tasks that decomposed from order. Most recent researchers e.g. Wu et al. \cite{Wu2013}, describe this operation procedure in cloud manufacturing as a tri-group user model that contains:\begin{inparaenum}[1)]
\item users/customers,
\item application providers and
\item physical resource providers.
\end{inparaenum}
Inspired by this model, we design the original operation mode shown in \autoref{fig:originmode} as the basis.
\begin{figure}[htbp]
    \centering
    \resizebox{0.9\textwidth}{!}{\input{figures/origin_mode}}
    \caption{Original mode}
    \label{fig:originmode}
\end{figure}
In this mode, individual executes activities that interact with others depicted by object flow(full lines) and information flow(dashed lines). The demander publish order that can be described by an activity-on-node(AON) network where the node represent the task and the arc the precedence relation. Each task needs to be performed with pre-determined configuration of resources. Hence, even after response and assignment procedure, the selected resource cannot start to process the task until all of other selected resources are ready, we call this procedure as resource cooperation and what each resource actually process is the task-part, which is a virtual segmentation of one task, it just like if we run one program in cloud computing platform, we actually use some quota of provider A's DB and some quota of provider B's CPU, we can consider these as task-parts. Product, the performance result after the processing and assembly procedure, will be delivered to demander, then demander change the rank value of the selected resource owners according to the review of the product. Cooperation procedure is necessary because of resource capacity is limited, but task-parts belonging to one task should be processed simultaneously to make sure the required resource capacities are available. We call the task-part is active when being processed, semi-active when selected resource is cooperating, inactive when this part is just assigned to the job queue.

\subsubsection{Assumptions} % (fold)
\label{ssub:assumptions_nomenclature}
To scope our research, we make some assumptions as follows for the original mode, while in other extension, some of the assumptions will be modified.
\begin{compactitem}
\item Each single task should be assembled by its task-parts, and these parts should be processed simultaneously;
\item The quality of product is determined by the worst quality of the selected resource;
\item Resource are renewable that the available capacity will be restored when the processing procedure finished;
\item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
\item Cooperate and processing procedure cannot be interrupted;
\item Provider can only schedule task-parts in inactive status.
\end{compactitem}

@@

	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$, determined by order and some assignment procedure\\

@@

$(i,j,k,l,\alpha)$. When in scheduling procedure, we omit subscript $i$ for some reasons in \autoref{sub:schedule_the_jobs_in_machine}.

@@

\subsection{Individual decisions in original mode} % (fold)
\label{sub:interactions_and_decisions}
\subsubsection{Provider respond to type-matched task}
\label{subs:Response_for_type_matched_task}
A provider makes decision at time $\tau\ge r_i$ to respond  to task if the belonging resource $mr_k$ was type-matched with $t_{ij}$ ($P(mr_k)\in\mathcal{A}_{ij}$). If $A_{k,\tau} \ge q_{\alpha,ij}$, the provider will respond to the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{ij,\tau}$. If $mr_k$ is finally selected, available capacity of $mr_k$ will change to $A_{k,\tau} := A_{k,\tau} - q_{\alpha,ij}$. This available capacity will be restored back to after the finish of $t_{ij}$ part.

\subsubsection{Demander select from resource candidates}
\label{subs:select_resource_candidates}
A demander makes decision about resource selection from $\mathcal{R}_{ij,\tau}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$. Without loss of generality, we suppose at time $\tau \ge r_i$, the decision-making of demander can be described as follows,
\begin{equation}
\max_{\forall \bm{k}}\left( \delta_{\bm{k}},
R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
\right) \label{eq:selectresaim}
\end{equation}
\begin{numcases}{\text{s.t.}}
q_{\alpha,ij} \le C_{k_{\alpha},\tau} & $\alpha\in\mathcal{A}_{ij}$\label{eq:rescaplimit}\\
\mathcal{R}_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & $\alpha\in\mathcal{A}_{ij}$\label{eq:restypeabstract}\\
\mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \label{eq:nrc}\\
\bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right] & \label{eq:decisionvectork}\\
k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &$\alpha\in\mathcal{A}_{ij}$ \label{eq:decisionvark}
\end{numcases}

The multi-objective in \autoref{eq:selectresaim} aims at high quality, high resource owner rank and low waiting queue length. \autoref{eq:rescaplimit} ensures that resource capacity is capable to process the task part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variables, the demander should make decision to select resources in each type.

@@

\subsection{Incubation mode} % (fold)
\label{sub:incubation_mode}
Incubation mode is one extension on the original mode, the purpose of this mode is to remove the cooperation and assembly procedure in advance by gathering types of resources with certain quota into manufacturing service, which will be incubated as shown in \autoref{fig:serviceincubatemode}.
\begin{figure}[htbp]
    \centering
    \resizebox{0.7\textwidth}{!}{\input{figures/service-incubate}}
    \caption{Incubation mode}
    \label{fig:serviceincubatemode}
\end{figure}
After the finish of task-part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such a task-specified service for the future performance.

The first thing of incubation is to publish a job named \textbf{service-call}, which is similar to task except for the capacity dominance feature , which means capacity of selected resource will not be restored after the performance of a service-call. The process result of one service-call is manufacturing \textbf{service}, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resources of a same type to make contributions to the formation of one service. No more cooperation and assembly procedure are one pro of service, and product quality will no longer be restricted to the worst quality of resources for the complementary effect, while the cons of service include that service can only perform specified task.
Now we can classify task and service-call into \textbf{job}, resource and service into \textbf{machine} for the follow discuss.

\subsubsection{Provider respond to type-matched job} % (fold)
\label{ssub:response_in_type_matched_resource}
Apart from $mr_k$ respond to $t_{ij}$ as we explained in \autoref{subs:Response_for_type_matched_task}, there are 2 other cases in incubation mode:
\begin{asparaenum}
\item $mr_k$ respond to $sc_l$
\suspend{asparaenum}
If $mr_k$ was type-matched with $sc_l$ ($P(mr_k)\in\mathcal{A}_l$), as long as $C_{k,\tau}> 0$, provider of $mr_k$ will respond to the service-call. If $mr_k$ was finally selected, both available capacity and capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and these capacity will not be restored even after the finish of $sc_l$ part. Provider of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{l,\tau}$.
\resume{asparaenum}
\item $ms_l$ respond to $t_{ij}$
\end{asparaenum}
Service is task-oriented machine, so if type-matched ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of it will respond to $t_{ij}$ as soon as possible, demander will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.

@@

Similar to other situations, \autoref{eq:combaim} is a multi-objective function that aims at high quality, high rank and low waiting queue length. \autoref{eq:optk} and \autoref{eq:optl} are the optimal decision in independent conditions, \autoref{eq:temprank}, \autoref{eq:templength} and \autoref{eq:tempqualitystart} are the virtual rank value, virtual queue length and virtual quality value that are set in the worst cases.\autoref{eq:tempqualitystart}--\ref{eq:tempqualityend} are the virtual quality value calculation procedure. \autoref{eq:newdicisionvariable} is the decision to choose one of these two partial optimal decision.

@@

In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{(s)}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}}$. Since the task in $\mathcal{L}^{(s)}_{k,\tau_0},\mathcal{H}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, we ignore the type subscript $\alpha$ because all the job assigned here are already type-matched. The schedule model is:

@@

% \subsection{Tricky problem} % (fold)
% \label{sub:tricky_problems}
% Even though the scheduling procedure exclude the interference of service-call, one tricky problem will occur that it will block some tasks from being processed. Suppose that $t_{i1}$ and $t_{i2}$ both need resource $mr_1$ and $mr_2$, as shown in \autoref{fig:joblock},
% \begin{figure}[htbp]
% 	\centering
% 	\resizebox{.75\textwidth}{!}{\input{figures/job-lock}}
% 	\caption{Simple illustration of job lock problem}
% 	\label{fig:joblock}
% \end{figure}
% $t_{i2}$ is semi-active in $mr_2$ and inactive in $mr_1$, while $t_{i1}$ is semi-active in $mr_1$ and inactive in $mr_2$, however, there is no more space for inactive tasks to stack in, so no matter how long the resource will wait, $t_{i1}$ and $t_i2$ will not be processed and they will block the other tasks from being processed.

### 2016-09-09 discussion.tex

\section{Acknowledgments} % (fold)
\label{sec:acknowledgments}
This work is supported by the National Natural Science Foundation of China (No. 71571161), and the National High Technology Research and Development Program of China (863 Program) (No. 2015AA042101). 
% section acknowledgments (end)

>>>>

\section{Acknowledgments} % (fold)
\label{sec:acknowledgments}
This work is supported by the National Natural Science Foundation of China (No. 71571161), the National High Technology Research and Development Program of China (863 Program) (No. 2015AA042101), and the Youth Funds of the Key Laboratory of Advanced Manufacturing Technology of Zhejiang Province(No. 2015QN01). 
% section acknowledgments (end)

### 2016-09-09 figures/origin_mode.tex

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
circle/.style={
rectangle,minimum size=1em,rounded corners=0.5em,
draw=black
}
]
\matrix[row sep=0.5em,column sep=2em] {
% First row:
\node (order) {Demander};& \node (task) [square]{Publish Orders}; &  & \node (select) [square]{Selection}; & & &  \node (finish) {Product}; \\
\node (start1) {}; & & & & & & \node (stop1) {}; \\
\node (plt) {Platform} ; & &  \node (tb) [square] {Task Hub} ; & \node (candidate) [square] {Resource Candidates} ; & \node (coop) [square] {Cooperate Resources}; & \node (combine) [square] {Task Assembly};\\
\node (start2) {}; & & & & & & \node (stop2) {}; & \\
\node (provider) {Provider};  & \node (resource) [square]{Provide Resources}; & \node (response) [square] {Response for Task}; & \node (add) [square]{Add to Candidates}; & \node (match) [square]{Assign Task}; & \node (process) [square] {Processing Task-part};  &\\
};
\draw[dotted,thick] (start1.west) -- (stop1.east) (start2.west) -- (stop2.east);
\path[->,dashed] (task.east) edge (tb.north) (tb) edge (response) (add) edge (candidate) (candidate) edge (select) (match) edge (coop) (coop.east) edge (process.west);
\path[->] (response) edge (add) (select.east) edge (match.west) (process) edge (combine) (combine.north) edge (finish.west);
% \path (order) edge[->] (task) (task) edge[->] (match) (match) edge[->] (coord) (coord) edge[->] (process) (process) edge[->] (finish) (provider) edge[->] (resource) (resource) edge[->] (match);
\end{tikzpicture}

>>>>

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
circle/.style={
rectangle,minimum size=1em,rounded corners=0.5em,
draw=black
}
]
\matrix[row sep=0.5em,column sep=2em] {
% First row:
\node (order) {Demander};& \node (task) [square]{Publish Orders}; &  & \node (select) [square]{Selection}; & & &  \node (finish) {Product}; \\
\node (start1) {}; & & & & & & \node (stop1) {}; \\
\node (plt) {Platform} ; & &  \node (tb) [square] {Task Hub} ; & \node (candidate) [square] {Resource Candidates} ; & \node (coop) [square] {Cooperate Resources}; & \node (combine) [square] {Task Assembly};\\
\node (start2) {}; & & & & & & \node (stop2) {}; & \\
\node (provider) {Provider};  & \node (resource) [square]{Provide Resources}; & \node (response) [square] {Respond to the Task}; & \node (add) [square]{Add to Candidates}; & \node (match) [square]{Assign Task}; & \node (process) [square] {Processing Task-part};  &\\
};
\draw[dotted,thick] (start1.west) -- (stop1.east) (start2.west) -- (stop2.east);
\path[->,dashed] (task.east) edge (tb.north) (tb) edge (response) (add) edge (candidate) (candidate) edge (select) (match) edge (coop) (coop.east) edge (process.west);
\path[->] (response) edge (add) (select.east) edge (match.west) (process) edge (combine) (combine.north) edge (finish.west);
% \path (order) edge[->] (task) (task) edge[->] (match) (match) edge[->] (coord) (coord) edge[->] (process) (process) edge[->] (finish) (provider) edge[->] (resource) (resource) edge[->] (match);
\end{tikzpicture}

### 2016-09-09 figures/scheduleChart.tex

\fill[blue!20!,yshift=19.5cm] (6cm,4cm) rectangle (7cm,5cm);
\draw[yshift=19.5cm] (3cm,0) rectangle (6cm,3cm) (6cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,4.5cm) (3cm,3cm) rectangle (6cm,3.5cm)  (4.5cm,1.6cm) node{$t_3$} (7cm,4.5cm) node{$sc_2$} (10.5cm,1.8cm) node{$t_2$} (2cm,2.25cm) node{$t_4$} (4.5cm,3.25cm) node{$t_5$};
\draw[dotted,yshift=19.5cm] (0,5cm) -- (7cm,5cm) (3cm,4cm) -- (15cm,4cm) (7cm,0) -- (7cm,5cm) (8cm,4cm) -- (8cm,3.5cm);
\draw[yshift=13cm] (0,0) rectangle (7cm,2.5cm) (7cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (1cm,2.5cm) rectangle (3cm,3.5cm)  (3.5cm,1.35cm) node{$t_1$} (7.5cm,4.5cm) node{$sc_2$} (10.5cm, 1.35cm) node{$t_2$}  (2cm,3cm) node{$t_4$};
\draw[dotted,yshift=13cm] (0,5cm) -- (7cm,5cm) (0,4cm) -- (15cm,4cm) (7cm,5cm) -- (7cm,0) (8cm,5cm) -- (8cm,0);
\draw[yshift=6.5cm] (0,0) rectangle (7cm,3.5cm) (7cm,2cm) rectangle (8cm,5cm) (3cm,3.5cm) rectangle (6cm,5cm) (3.5cm,1.85cm) node{$t_1$} (7.5cm,3.5cm) node{$sc_2$} (4.5cm,4.25cm) node{$t_5$};
\draw[dotted,yshift=6.5cm] (0,5cm) -- (7cm,5cm) (8cm,2cm) -- (15cm,2cm) (8cm,0) -- (8cm,2cm);
\draw (0,3.5cm) rectangle (1cm,5cm) (3cm,0) rectangle (6cm,2.5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,3cm) (4.5cm, 1.35cm) node {$t_3$} (0.5cm,4.3cm) node{$sc_1$} (10.5cm,1.8cm) node{$t_2$} (2cm,1.5cm) node{$t_4$};
\draw[dotted] (0,3.5cm) -- (15cm,3.5cm) (1cm,0) -- (1cm,3.5cm);
\end{tikzpicture}

>>>>

\fill[blue!20!,yshift=19.5cm] (6cm,4cm) rectangle (7cm,5cm);
\draw[yshift=19.5cm] (3cm,0) rectangle (6cm,3cm) (6cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,4.5cm) (3cm,3cm) rectangle (6cm,3.5cm)  (4.5cm,1.6cm) node{$t_3$} (7cm,4.5cm) node{$sc_2$} (10.5cm,1.8cm) node{$t_2$} (2cm,2.25cm) node{$t_4$} (4.5cm,3.25cm) node{$t_5$};
\draw[dotted,yshift=19.5cm] (0,5cm) -- (7cm,5cm) (3cm,4cm) -- (15cm,4cm) (7cm,0) -- (7cm,5cm) (8cm,4cm) -- (8cm,3.5cm);
\draw[yshift=13cm] (0,0) rectangle (7cm,2.5cm) (7cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (1cm,2.5cm) rectangle (3cm,4.5cm)  (3.5cm,1.35cm) node{$t_1$} (7.5cm,4.5cm) node{$sc_2$} (10.5cm, 1.35cm) node{$t_2$}  (2cm,3.5cm) node{$t_4$};
\draw[dotted,yshift=13cm] (0,5cm) -- (7cm,5cm) (3cm,4cm) -- (15cm,4cm) (7cm,5cm) -- (7cm,0) (8cm,5cm) -- (8cm,0);
\draw[yshift=6.5cm] (0,0) rectangle (7cm,3.5cm) (7cm,2cm) rectangle (8cm,5cm) (3cm,3.5cm) rectangle (6cm,5cm) (3.5cm,1.85cm) node{$t_1$} (7.5cm,3.5cm) node{$sc_2$} (4.5cm,4.25cm) node{$t_5$};
\draw[dotted,yshift=6.5cm] (0,5cm) -- (7cm,5cm) (8cm,2cm) -- (15cm,2cm) (8cm,0) -- (8cm,2cm);
\draw (0,3.5cm) rectangle (1cm,5cm) (3cm,0) rectangle (6cm,2.5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,3cm) (4.5cm, 1.35cm) node {$t_3$} (0.5cm,4.3cm) node{$sc_1$} (10.5cm,1.8cm) node{$t_2$} (2cm,1.5cm) node{$t_4$};
\draw[dotted] (0,3.5cm) -- (15cm,3.5cm) (1cm,0) -- (1cm,3.5cm);
\end{tikzpicture}

### 2016-09-09 head.tex

\title{The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture
%Cloud Manufacturing Ecosystem - Scheduling And Evolving
}

\author[add1]{Shengkai Chen}
\author[add1,add2]{Shuiliang Fang\corref{cor1}}
% \ead{me_fangsl@zju.edu.cn}
% \address[label1]{ZJU}
% \address[label1]{Address One}
\address[add2]{The State Key Laboratory of Fluid Power Transmission and Control, College of Mechanical Engineering, Zhejiang University, Hangzhou, 310027, China}
\address[add1]{Key Laboratory of Advanced Manufacturing Technology of Zhejiang Province, College of Mechanical Engineering, Zhejiang University, Hangzhou , 310027, China}
% \author[a,b,*]{Third Author}

@@

\cortext[cor1]{Corresponding author. Tel.: +86-135-8880-3980; Email: me\_fangsl@zju.edu.cn}

@@

\begin{keyword}
Cloud manufacturing ecosystem \sep
Decision making\sep
Operation mode\sep
Ecosystem evolution\sep
Agent-based simulation

>>>>

\title{Operation Mode Study in Cloud Manufacturing Ecosystem
%Cloud Manufacturing Ecosystem - Scheduling And Evolving
}

\author[add1]{Shengkai Chen}
\author[add2,add1]{Shuiliang Fang\corref{cor1}}
\author[add2,add1]{Tao Peng}
% \ead{me_fangsl@zju.edu.cn}
% \address[label1]{ZJU}
% \address[label1]{Address One}
\address[add2]{The State Key Laboratory of Fluid Power Transmission and Control, College of Mechanical Engineering, Zhejiang University, Hangzhou, 310027, China}
\address[add1]{Key Laboratory of Advanced Manufacturing Technology of Zhejiang Province, College of Mechanical Engineering, Zhejiang University, Hangzhou , 310027, China}
% \author[a,b,*]{Third Author}

@@

\cortext[cor1]{Corresponding author. Email: me\_fangsl@zju.edu.cn}

@@

\begin{keyword}
Cloud manufacturing ecosystem \sep
Decision-making\sep
Operation mode\sep
Ecosystem evolution\sep
Agent-based simulation
